Classless Java

### 2015-11-11 paper/sections/RelatedWork.tex
related work on fluent interfaces

\paragraph{Meta-programming techniques}
- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}

@@

\paragraph{Fluent Interfaces}

Talk about existing libraries that use fluent interfaces (do any of
those use any code generation to assist in the implementation?).

>>>>

\subsection{Meta-programming techniques}
- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}

@@

\subsection{Fluent Interfaces}
Talk about existing libraries that use fluent interfaces (do any of
those use any code generation to assist in the implementation?).

Since the style of fluent interfaces was invented in Smalltalk as method
cascading, more and more languages came to support fluent interfaces, including
JavaScript, Java, C++, D, Ruby, Scala, etc. For most languages, to create fluent
interfaces, programmers have to either handwritten everything or create a
wrapper around the original non-fluent interfaces, using \textbf{this}. In Java,
several libraries help create fluent APIs easily (by code generation), including
jOOQ, op4j, fluflu, JaQue, etc. These libraries have given us hints on the
implementation of fluent setters in ClassLess Java.
